Assignment 4

### 2015-03-09 rmtw/a4/latex8.tex
sdf

\subsection{first hypothesis}
Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum teset was chosen instead of the Student's T-test as the final test. The data used for the WMW test was the efficiency of each participant. The result of the WMW test was W=250, p=0.1063 and with the significance level of 536 H0 is rejected.

>>>>

\subsection{first hypothesis}
Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test. The data used for the WMW test was the efficiency of each participant. The result of the WMW test was W=250, p=0.1063 and with the significance level of 536 H0 is rejected.
